Calendar-based graphics for visualising people's daily schedules

### 2017-09-12 main.Rmd
used wqy-microhei in showtext
should fix up the chinese fonts issue in adobe

Most countries have adopted this western calendar layout, while the languages used for week day and month would be different across countries. We also offer languages other than English for text labelling. Figure \ref{fig:chn} shows the same plot as Figure \ref{fig:boxplot} labelled using simplified Chinese characters.

@@

```{r chn, dev.args = list(family = "GB1"), fig.height = 6.5, fig.cap = "(ref:chn-cap)"}
```

>>>>

Most countries have adopted this western calendar layout, while the languages used for week day and month would be different across countries. We also offer languages other than English for text labelling. Figure \ref{fig:chn-embedded} shows the same plot as Figure \ref{fig:boxplot} labelled using simplified Chinese characters.

@@

<!-- ```{r chn, dev.args = list(family = "wqy-microhei"), fig.height = 6.5, fig.cap = "(ref:chn-cap)"} -->
<!-- ``` -->

```{r chn-embedded, fig.cap = "(ref:chn-cap)"}
include_graphics("figure/chn-1-embedded.pdf")
```
